### 2022-06-24 proposal-documents/white-paper/white-paper-general-preproposal.tex

\section*{Workscopes in Brief}
\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=0.5in]
    \item\textbf{X.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
            \item\textit{x.}
            \item\textit{x.}
        \end{enumerate}
    \item\textbf{X.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[resume,topsep=3pt,itemsep=1ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.25in]
            \item\textit{x.}
            \item\textit{x.}
        \end{enumerate}
\end{enumerate}

@@

\section*{Research Workscopes \& Tasks}
\subsection*{Research activities}

\subsection*{Workscope 1 - Title}
\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{First task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
    \item\textit{Second task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
\end{enumerate}

\vspace{0.05in}

\noindent\textit{Through this Workscope, we will \ldots.}

\subsection*{Workscope 2 - Title}
\begin{enumerate}[resume,topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Next task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
    \item\textit{Next task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
\end{enumerate}

\vspace{0.05in}

\noindent\textit{Through this Workscope, we will \ldots.}

>>>>

\section*{Workscopes in Brief}
\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{Identify lessons learned.}
            \item\textit{Develop future work.}
            \item\textit{Reproducibility \& validation.}
        \end{enumerate}
\end{enumerate}

@@

\section*{Research Workscopes \& Tasks}
\subsection*{Research activities}
Overview.

\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{Identify lessons learned.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{Develop future work.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{Reproducibility \& validation.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will wrapup the major findings of project activities and pursue new avenues of research with colleagues in the field.}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

### 2022-06-24 proposal-documents/white-paper/white-paper-phd-proposal.tex

\section*{Importance and Relevance to Objectives} 
\subsection*{Background}

@@

\section*{Research Workscopes \& Tasks}
\subsection*{Research activities}

\subsection*{Workscope 1 - Title}
\begin{enumerate}[topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{First task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
    \item\textit{Second task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
\end{enumerate}

\vspace{0.05in}

\noindent\textit{Through this Workscope, we will \ldots.}

\subsection*{Workscope 2 - Title}
\begin{enumerate}[resume,topsep=0pt,itemsep=0ex,partopsep=1ex,parsep=1ex,label=\textit{Task \Roman*.},align=left,leftmargin=0.5in]
    \item\textit{Next task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
    \item\textit{Next task.}
        \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
            \item Details.
        \end{enumerate}
\end{enumerate}

\vspace{0.05in}

\noindent\textit{Through this Workscope, we will identify plant systems vulnerable to cyberattacks applying a risk-informed approach and operate the reactor to collect relevant plant data.}

\section*{Logical Path to Work Accomplishment. Major Deliverables and Outcomes.} 
The following outcomes are anticipated - 
\begin{enumerate}[leftmargin=*,topsep=0pt,itemsep=-0.75ex,partopsep=1ex,parsep=1ex,label=(\arabic*)]
    \item
    \item
    \item
    \item Identify lessons learned and engage in future pathways and partnerships.
\end{enumerate}

>>>>

\section*{Workscopes in Brief}
\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
            \item\textit{.}
        \end{enumerate}
\end{enumerate}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{Identify lessons learned.}
            \item\textit{Develop future work.}
            \item\textit{Reproducibility \& validation.}
        \end{enumerate}
\end{enumerate}
\section*{Importance and Relevance to Objectives} 
\subsection*{Background}

@@

\section*{Research Workscopes \& Tasks}
\subsection*{Research activities}
Overview.

\begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - , })
        \begin{enumerate}[series=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{.} (\textit{Lead - ; Support - })
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will \ldots}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}

\begin{enumerate}[resume,topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=\textbf{Workscope \arabic* -},align=left,leftmargin=*]
    \item\textbf{Crosscutting.} (\textit{Lead - ; Support - Full team})
        \begin{enumerate}[resume=innerlist,topsep=3pt,itemsep=1.5ex,partopsep=1ex,parsep=-1ex,label=\textit{Task \Roman*.},align=left,leftmargin=-0.50in]
            \item\textit{Identify lessons learned.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{Develop future work.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
            \item\textit{Reproducibility \& validation.}
                \begin{enumerate}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,label=(\arabic*),leftmargin=0.15in]
                    \item Details.
                    \item Details.
                \end{enumerate}
        \end{enumerate}
\end{enumerate}

\paragraph*{Motivation}

\paragraph*{Goals}
\textit{Through this Workscope, we will wrapup the major findings of project activities and pursue new avenues of research with colleagues in the field.}

\paragraph*{Investigator duties}
\begin{itemize}[topsep=0pt,itemsep=-0.5ex,partopsep=1ex,parsep=1ex,leftmargin=*]
    \item[].
    \item[].
    \item[].
\end{itemize}
